Extreme value analysis for the sample autocovariance matrices of heavy-tailed multivariate time series

### 2017-08-21 papers/Anja/PaperBody.tex
Updated the thesis manuscript.

@@

@@

\limsup_{\nto}\P\big(\|\bfV- V_{L_j}\bfe_{L_j}\|_{\ell_2}>\delta\big)&\le &

@@

\begin{align} \nonumber \boldsymbol{\sigma}&= \mbox{diag}\left(\left(

@@

  \prod\limits_{(m,n) \in \Lambda_{\mathbf{i},\mathbf{j},\mathbf{t}}^c}\ex^{\eta_{m,n}(\psi_{i_1-m,t_1-n}+\psi_{j_1-m,t_1-n})} \\ \vdots \\ \prod\limits_{(m,n) \in \Lambda_{\mathbf{i},\mathbf{j},\mathbf{t}}^c}\ex^{\eta_{m,n}(\psi_{i_d-m,t_d-n}+\psi_{j_d-m,t_d-n})}

@@

\right)'\right)\cdot \left(\begin{matrix}
                   \prod\limits_{(m,n) \in \Lambda_{\mathbf{i},\mathbf{j},\mathbf{t}}}\ex^{\eta_{m,n}(\psi_{i_1-m,t_1-n}+\psi_{j_1-m,t_1-n})} \\ \vdots \\ \prod\limits_{(m,n) \in \Lambda_{\mathbf{i},\mathbf{j},\mathbf{t}}}\ex^{\eta_{m,n}(\psi_{i_d-m,t_d-n}+\psi_{j_d-m,t_d-n})}

@@

 \right)\\
\label{Eq:factors:sigma} &=: \mathbf{A}\, \mathbf{Z},
\end{align}

@@

\begin{align}\label{Eq:theta:law:1}
  \P((\Theta^{i}_t)_{t=0,\ldots,n}
  \in B)=\sum_{(u,v) \in \Lambda_i^{(0)}}\frac{1}{|\Lambda_i^{(0)}

@@

\end{align}

@@

\begin{align}  
&\P(( \Theta^{ij}_t)_{t=0,\ldots,n} \in B) \nonumber \\
 \label{Eq:theta:law:2}=&\sum_{(u,v) \in

@@

%and the random variables $\ex^{\eta_{u,v}^{(u,v)}}$,$(\ex^{\eta_{l,m}^{(u,v)}})_{(l,m)\neq(u,v)}$, $(\tilde{Z}_{i,t},\tilde{Z}_{j,t})_{t=0, \ldots, n}$ have joint $\nu_{\alpha} \otimes (\otimes_{(l,m)\neq(u,v)} P^{\ex^{\eta}}) \otimes (\otimes_{t=0, \ldots, n}P^{(Z_{i},Z_{j})})$-density 
%\begin{eqnarray*}&& f^{(u,v)}(y_{u,v},(y_{l,m})_{(l,m) \neq (u,v)}, (z_{i,t},z_{j,t})_{t=0, \ldots, n})\\
%&=&\frac{\I(\prod_{(l,m)}y_{l,m}^{\psi_{i-l,-m}+\psi_{j-l,-m}}|z_{i,0}z_{j,0}|>1)}{\E[(\prod_{(l,m)\neq(u,v)}\ex^{\eta_{l,m}^{(u,v)}(\psi_{i-l,-m}+\psi_{j-l,-m})}|\tilde{Z}_{i,0}\tilde{Z}_{j,0}|)^{\alpha/\psi^{ij}}]},
%\end{eqnarray*}

@@

&=& \label{Eq:mu:X} c\,\E\left[\tilde{\mu}_n^{\boldsymbol{\sigma}^{ij}}\left(\times_{t=0}^n \left(B_t \bigg/ \left(Z_{it}Z_{jt}\prod_{(u,v) \in \Lambda_{i,j,n}^c}\ex^{\eta_{u,v}(\psi_{i-u,t-v}+\psi_{j-u,t-v})}\right)\right)\right)\right] 

@@

 \tilde{\mu}^{\boldsymbol{\sigma}^{ij}}_n(B)&=& c \sum_{s=0}^n \int_0^\infty \P\bigg(\bigg(\I(\psi_{i-u,t-v}+\psi_{j-u,t-v}=\psi^{ij} \, \forall\, (u,v) \in \Lambda_{i,j}^{(s)})z^{\psi^{ij}}\\
 && \hspace{1.7cm} \prod_{(u,v) \in \Lambda_{i,j,n} \setminus \Lambda_{i,j}^{(s)}}\ex^{\eta_{u,v}(\psi_{i-u,t-v}+\psi_{j-u,t-v})}\bigg)_{0 \leq t \leq n} \in B\bigg)\nu_{\alpha}(dz)\\
 &=& c \sum_{s=0}^n \int_0^\infty \P\bigg(\bigg(\I(t=s)z^{\psi^{ij}}\prod_{(u,v) \in \Lambda_{i,j,n} \setminus \Lambda_{i,j}^{(s)}}\ex^{\eta_{u,v}(\psi_{i-u,t-v}+\psi_{j-u,t-v})}\bigg)_{0 \leq t \leq n} \in B\bigg)\nu_{\alpha}(dz),

@@

\begin{eqnarray*} && \tilde{\mu}^{\boldsymbol{\sigma}^{ij}}_n(B) \\
&=&\hspace{-0.3cm} \sum_{(u,v) \in \Lambda_{i,j,n}}\int_0^\infty \P\bigg(\bigg(\I((u,v) \in \Lambda_{i,j}^{(t)})z^{\psi^{ij}}\prod_{\substack{(\tilde{u},\tilde{v}) \in \Lambda_{i,j,n} \\ (\tilde{u},\tilde{v}) \neq (u,v)}}\ex^{(\psi_{i-\tilde{u},t-\tilde{v}}+\psi_{j-\tilde{u},t-\tilde{v}})\eta_{\tilde{u},\tilde{v}}}\bigg)_{t=0, \ldots ,n} \in B \bigg)\nu_{\alpha}(dz).\end{eqnarray*}                                                                                                

@@

\begin{align*} & \mu^{\bfX^{ij}}_n(B)/c\\
= &\sum_{(u,v) \in \Lambda_{i,j}^{(0)}}\int\limits_0^\infty \P\bigg((\I((u,v) \in \Lambda_{i,j}^{(t)})z^{\psi^{ij}}\prod\limits_{(\tilde{u},\tilde{v}) \neq (u,v)}\ex^{(\psi_{i-\tilde{u},t-\tilde{v}}+\psi_{j-\tilde{u},t-\tilde{v}})\eta_{\tilde{u},\tilde{v}}} Z_{it}Z_{jt})_{t=0, \ldots ,n} \in B \bigg)\nu_{\alpha}(dz)\\
= &\sum_{(u,v) \in \Lambda_{i,j}^{(0)}}\int\limits_0^\infty \P\bigg((\I((u,v) \in \Lambda_{i,j}^{(t)})z^{\psi^{ij}}X_{it}X_{jt}\ex^{-\psi^{ij}\eta_{u,v}})_{t=0, \ldots ,n} \in B \bigg)\nu_{\alpha}(dz),\end{align*}

@@

\begin{eqnarray*} &&  \sum_{(u,v) \in \Lambda_{i,j}^{(0)}}\E\left[\int_0^\infty \I\left(\left(\I((u,v) \in \Lambda_{i,j}^{(t)})z^{\psi^{ij}}X_{it}X_{jt}\ex^{-\psi^{ij}\eta_{u,v}}\right)_{t=0, \ldots, n} \in B\right)\nu_\alpha(dz)\right]  \\
&=& \sum_{(u,v) \in \Lambda_{i,j}^{(0)}}\E\left[\int_0^\infty \I\left(\left(\I((u,v) \in \Lambda_{i,j}^{(t)})y \frac{X_{it}X_{jt}}{|X_{i0}X_{j0}|}\right)_{t=0, \ldots, n} \in B\right)|X_{i0}X_{j0}|^{\alpha/\psi^{ij}}\ex^{-\alpha \eta_{u,v}}\nu_{\frac{\alpha}{\psi^{ij}}}(dy)\right].

@@

\ex^{2r\sum_{(k,l)\in \Gamma_\xi}\psi_{kl}(\eta_{i-k,-l}+\eta_{i-k,h-l})}\big]\big)^{1/r} \big(\E\big[ \ex^{2s\sum_{(k,l) \not \in \Gamma_\xi}\psi_{kl}(\eta_{i-k,-l}+\eta_{i-k,h-l})}\big]\big)^{1/s}\,,

@@

\std \Big(\la_{(i)}\big((\xi_{kl,\alpha/2} \I((k,l)\in \Gamma_p))_{1\le k,l\le p}\big)\Big)_{i=1,\ldots,p} \,,\nonumber\\

@@

@@

>>>>

\begin{small}

@@

\end{small}

@@

&&\limsup_{\nto}\P\big(\|\bfV- V_{L_j}\bfe_{L_j}\|_{\ell_2}>\delta\big) \\

@@

\begin{equation}
  \label{Eq:factors:sigma}
  \boldsymbol\sigma = \mathbf A\, \mathbf Z
  \mathbf A
  &=&
  \mbox{diag}\left(\left(

@@

        \prod\limits_{(m,n) \in \Lambda_{\mathbf{i},\mathbf{j},\mathbf{t}}^c}
        \ex^{\eta_{m,n}(\psi_{i_1-m,t_1-n}+\psi_{j_1-m,t_1-n})} \\
        \vdots \\
        \prod\limits_{(m,n) \in \Lambda_{\mathbf{i},\mathbf{j},\mathbf{t}}^c}
        \ex^{\eta_{m,n}(\psi_{i_d-m,t_d-n}+\psi_{j_d-m,t_d-n})}

@@

\right)'\right), \\
\mathbf Z
&=&
\left(
    \prod\limits_{(m,n) \in \Lambda_{\mathbf{i},\mathbf{j},\mathbf{t}}}
    \ex^{\eta_{m,n}(\psi_{i_1-m,t_1-n}+\psi_{j_1-m,t_1-n})} \\
    \vdots \\
    \prod\limits_{(m,n) \in \Lambda_{\mathbf{i},\mathbf{j},\mathbf{t}}}
    \ex^{\eta_{m,n}(\psi_{i_d-m,t_d-n}+\psi_{j_d-m,t_d-n})}

@@

\right).

@@

  && \P((\Theta^{i}_t)_{t=0,\ldots,n} \in B) \label{Eq:theta:law:1} \\
  &=&
  \sum_{(u,v) \in \Lambda_i^{(0)}}\frac{1}{|\Lambda_i^{(0)}

@@

  \nonumber

@@

  && \P(( \Theta^{ij}_t)_{t=0,\ldots,n} \in B) \label{Eq:theta:law:2} \\
  &=&
  \sum_{(u,v) \in

@@

@@

&=& \label{Eq:mu:X} c\,\E\left[\tilde{\mu}_n^{\boldsymbol{\sigma}^{ij}}\left(\times_{t=0}^n
    \left( {
      B_t Z_{it}^{-1} Z_{jt}^{-1}
      \over
      \prod_{(u,v) \in \Lambda_{i,j,n}^c}\ex^{\eta_{u,v}(\psi_{i-u,t-v}+\psi_{j-u,t-v})}
  }\right)
\right)\right] 

@@

 && \tilde{\mu}^{\boldsymbol{\sigma}^{ij}}_n(B) \\
 &=& c \sum_{s=0}^n \int_0^\infty \P\bigg[\bigg(\I(\psi_{i-u,t-v}+\psi_{j-u,t-v}=\psi^{ij} \, \forall\, (u,v) \in \Lambda_{i,j}^{(s)})z^{\psi^{ij}}\\
 && \prod_{(u,v) \in \Lambda_{i,j,n} \setminus \Lambda_{i,j}^{(s)}}\ex^{\eta_{u,v}(\psi_{i-u,t-v}+\psi_{j-u,t-v})}\bigg)_{0 \leq t \leq n} \in B\bigg]\nu_{\alpha}(dz)\\
 &=& c \sum_{s=0}^n \int_0^\infty \P\bigg[\bigg(\I(t=s)z^{\psi^{ij}} \\
 && \prod_{(u,v) \in \Lambda_{i,j,n} \setminus \Lambda_{i,j}^{(s)}}\ex^{\eta_{u,v}(\psi_{i-u,t-v}+\psi_{j-u,t-v})}\bigg)_{0 \leq t \leq n} \in B\bigg]\nu_{\alpha}(dz),

@@

  && \tilde{\mu}^{\boldsymbol{\sigma}^{ij}}_n(B) \\
  &=& \sum_{(u,v) \in \Lambda_{i,j,n}}\int_0^\infty \P\bigg[\bigg(\I((u,v) \in \Lambda_{i,j}^{(t)})z^{\psi^{ij}} \\
  && \prod_{\substack{(\tilde{u},\tilde{v}) \in \Lambda_{i,j,n} \\ (\tilde{u},\tilde{v}) \neq (u,v)}}\ex^{(\psi_{i-\tilde{u},t-\tilde{v}}+\psi_{j-\tilde{u},t-\tilde{v}})\eta_{\tilde{u},\tilde{v}}}\bigg)_{t=0, \ldots ,n} \in B \bigg]\nu_{\alpha}(dz).

@@

  && \mu^{\bfX^{ij}}_n(B)/c\\
  &=&
  \sum_{(u,v) \in \Lambda_{i,j}^{(0)}}\int\limits_0^\infty \P\bigg[(\I((u,v) \in \Lambda_{i,j}^{(t)})z^{\psi^{ij}} \\
  &&
  \prod\limits_{(\tilde{u},\tilde{v}) \neq (u,v)}\ex^{(\psi_{i-\tilde{u},t-\tilde{v}}+\psi_{j-\tilde{u},t-\tilde{v}})\eta_{\tilde{u},\tilde{v}}} Z_{it}Z_{jt})_{t=0, \ldots ,n} \in B \bigg]\nu_{\alpha}(dz)\\
  &=&
  \sum_{(u,v) \in \Lambda_{i,j}^{(0)}}\int\limits_0^\infty \P\bigg((\I((u,v) \in \Lambda_{i,j}^{(t)})z^{\psi^{ij}}X_{it}X_{jt}\ex^{-\psi^{ij}\eta_{u,v}})_{t=0, \ldots ,n} \in B \bigg)\nu_{\alpha}(dz),

@@

&&
\sum_{(u,v) \in \Lambda_{i,j}^{(0)}}\E\left[\int_0^\infty \I\left(\left(\I((u,v) \in \Lambda_{i,j}^{(t)})z^{\psi^{ij}}X_{it}X_{jt}\ex^{-\psi^{ij}\eta_{u,v}}\right)_{t=0, \ldots, n} \in B\right)\nu_\alpha(dz)\right]  \\
&=&
\sum_{(u,v) \in \Lambda_{i,j}^{(0)}}\E\bigg[\int_0^\infty \I\left(\left(\I((u,v) \in \Lambda_{i,j}^{(t)})y \frac{X_{it}X_{jt}}{|X_{i0}X_{j0}|}\right)_{t=0, \ldots, n} \in B\right) \\
&&
|X_{i0}X_{j0}|^{\alpha/\psi^{ij}}\ex^{-\alpha \eta_{u,v}}\nu_{\frac{\alpha}{\psi^{ij}}}(dy)\bigg].

@@

\ex^{2r\sum_{(k,l)\in \Gamma_\xi}\psi_{kl}(\eta_{i-k,-l}+\eta_{i-k,h-l})}\big]\big)^{1/r} \\
&&
\big(\E\big[ \ex^{2s\sum_{(k,l) \not \in \Gamma_\xi}\psi_{kl}(\eta_{i-k,-l}+\eta_{i-k,h-l})}\big]\big)^{1/s}\,,

@@

&& a_n^{-2}\Big(\la_{(i)} -n\,\E[X^2] 1(\alpha\in (2,4))\Big)_{i=1,\ldots,p} \\
&\std&
\Big(\la_{(i)}\big((\xi_{kl,\alpha/2} \I((k,l)\in \Gamma_p))_{1\le k,l\le p}\big)\Big)_{i=1,\ldots,p} \,,\nonumber

@@

\begin{footnotesize}

@@

\end{footnotesize}

### 2017-08-21 papers/DavisMikoschHeinyXie/PaperBody.tex
Updated the thesis manuscript.

\begin{example}\label{exam:additive}{\em
\begin{figure}[htb!]
  \centering
  \subfigure[]
{
    \includegraphics[scale=0.4]{eigen_sum.pdf}
    \label{fig:LamYao:a}
  }
  \subfigure[] {
    \includegraphics[scale=0.375]{eigen_sum_ratio.pdf}
    \label{fig:LamYao:b}
  }
  \caption{The largest eigenvalues of the sums of the squared autocovariance
    matrices compared with the sums of the largest eigenvalues of these matrices
    for the S\&P 500 data for different values $s_1$. The two values are surprisingly close to each other; mind the scale
of the $y$-axis. We also show their ratios.}
  \label{fig:LamYao}
\end{figure}
Recall the separable case from Example~\ref{exam:separable}, i.e.,
$h_{kl}=\theta_kc_l$, $k,l \ge 0$, where $(c_l)$, $(\theta_k)$ are
real sequences such that the conditions on $(h_{kl})$ in
Theorem~\ref{thm:mains} hold.
%Let $\alpha \in (0,2)$ and set
%\begin{equation*}
%\theta = (\theta_0, \theta_1,\theta_2,\ldots)' \quad \mbox{and} \quad
%c= (c_0,c_1,c_2, \ldots)'.
%\end{equation*}
Write $\Theta_{ij}=\theta_i \theta_j$. It is symmetric and has rank one; the only non-zero
eigenvalue is $\gamma_\theta(0)=\sum_{k=0}^\infty \theta_k^2$. Hence $\Theta$  is non-negative definite.
We get from \eqref{eq:m} that
\begin{equation*}
\M(s)=\gamma_c(s)\, \Theta, \quad s\ge 0\,,
\end{equation*}
where
\beao
\gamma_c(s)=\sum_{l=0}^\infty c_lc_{l+s}\,,\qquad s\ge 0\,.
\eeao
The matrix $\M(s)$ has the only non-zero eigenvalue $\gamma_c(s)\gamma_\theta(0)$.
The factors $(\gamma_c(s))$ can be positive or negative; they constitute the autocovariance \fct\ of a stationary linear process
with coefficients $(c_l)$.
Accordingly, $\M(s)$ is either non-negative or non-positive definite. %This explains why a symmetrization of $\M(s)$ is irrelevant.
Now we consider the non-negative definite matrix
\beao
\sum_{s=s_0}^{s_1} \M(s)\,\M(s)'= \sum_{s=s_0}^{s_1}\gamma_c^2(s)\,\Theta\Theta'\,.
\eeao
This matrix has rank $1$ and its largest eigenvalue is given by
\begin{equation*}
C_{c,\theta}(s_0,s_1)=\sum_{s=s_0}^{s_1}\gamma_c^2(s)\,\gamma_\theta^2(0)\,.
\end{equation*}
An application of
Proposition~\ref{prop:sumsmal} yields that the ordered eigenvalues of $a_{np}^{-4}\sum_{s=s_0}^{s_1}\A_n(s)\A_n(s)'$
are uniformly approximated by the quantities
\begin{equation}\label{eq:drtgdfg}
a_{np}^{-4} Z_{(i),np}^4 C_{c,\theta}(s_0,s_1)\,,\qquad  i=1,\ldots,p\,.
\end{equation}
Since
\beao
C_{c,\theta}(s_0,s_1)= \sum_{i=s_0}^{s_1} C_{c,\theta}(i,i)
\eeao
one gets the remarkable property that
\beao
&&a_{np}^{-4}\max_{i=1,\ldots,p} \Big| \la_{(i)}\Big(\sum_{s=s_0}^{s_1}\A_n(s)\A_n(s)'\Big)- Z_{(i),np}^4 C_{c,\theta}(s_0,s_1)\Big|\\
&=&a_{np}^{-4}\max_{i=1,\ldots,p} \Big|\sum_{s=s_0}^{s_1}\la_{(i)}(\A_n(s)\A_n(s)')- Z_{(i),np}^4 C_{c,\theta}(s_0,s_1)\Big|+o_P(1)\,.
\eeao
In particular, for $s_1\ge s_0$ we get the weak \con\ of the \pp es towards a PRM:
\beao
\sum_{i=1}^p \varepsilon_{a_{np}^{-4}\Big(\la_{i}\Big(\sum_{s=s_0}^{s_0}\A_n(s)\A_n(s)'\big)\,,\ldots,\la_{i}\big(\sum_{s=s_0}^{s_1}\A_n(s)\A_n(s)'\big)\Big)}
\std \sum_{i=1}^\infty \varepsilon_{\Gamma_i^{-4/\alpha} \Big(C_{c,\theta}(s_0,s_0),\ldots,C_{c,\theta}(s_0,s_1)\Big)}\,.
\eeao

>>>>

\begin{example}\label{exam:additive}{\em
\begin{figure}[htb!]
  \centering
  \subfigure[]
{
    \includegraphics[scale=0.4]{eigen_sum.pdf}
    \label{fig:LamYao:a}
  }
  \subfigure[] {
    \includegraphics[scale=0.375]{eigen_sum_ratio.pdf}
    \label{fig:LamYao:b}
  }
  \caption{The largest eigenvalues of the sums of the squared autocovariance
    matrices compared with the sums of the largest eigenvalues of these matrices
    for the S\&P 500 data for different values $s_1$. The two values are surprisingly close to each other; mind the scale
of the $y$-axis. We also show their ratios.}
  \label{fig:LamYao}
\end{figure}
Recall the separable case from Example~\ref{exam:separable}, i.e.,
$h_{kl}=\theta_kc_l$, $k,l \ge 0$, where $(c_l)$, $(\theta_k)$ are
real sequences such that the conditions on $(h_{kl})$ in
Theorem~\ref{thm:mains} hold.
%Let $\alpha \in (0,2)$ and set
%\begin{equation*}
%\theta = (\theta_0, \theta_1,\theta_2,\ldots)' \quad \mbox{and} \quad
%c= (c_0,c_1,c_2, \ldots)'.
%\end{equation*}
Write $\Theta_{ij}=\theta_i \theta_j$. It is symmetric and has rank one; the only non-zero
eigenvalue is $\gamma_\theta(0)=\sum_{k=0}^\infty \theta_k^2$. Hence $\Theta$  is non-negative definite.
We get from \eqref{eq:m} that
\begin{equation*}
\M(s)=\gamma_c(s)\, \Theta, \quad s\ge 0\,,
\end{equation*}
where
\beao
\gamma_c(s)=\sum_{l=0}^\infty c_lc_{l+s}\,,\qquad s\ge 0\,.
\eeao
The matrix $\M(s)$ has the only non-zero eigenvalue $\gamma_c(s)\gamma_\theta(0)$.
The factors $(\gamma_c(s))$ can be positive or negative; they constitute the autocovariance \fct\ of a stationary linear process
with coefficients $(c_l)$.
Accordingly, $\M(s)$ is either non-negative or non-positive definite. %This explains why a symmetrization of $\M(s)$ is irrelevant.
Now we consider the non-negative definite matrix
\beao
\sum_{s=s_0}^{s_1} \M(s)\,\M(s)'= \sum_{s=s_0}^{s_1}\gamma_c^2(s)\,\Theta\Theta'\,.
\eeao
This matrix has rank $1$ and its largest eigenvalue is given by
\begin{equation*}
C_{c,\theta}(s_0,s_1)=\sum_{s=s_0}^{s_1}\gamma_c^2(s)\,\gamma_\theta^2(0)\,.
\end{equation*}
An application of Proposition~\ref{prop:sumsmal} yields that the ordered eigenvalues of
\[
a_{np}^{-4}\sum_{s=s_0}^{s_1}\A_n(s)\A_n(s)'
\]

are uniformly approximated by the quantities
\begin{equation}\label{eq:drtgdfg}
a_{np}^{-4} Z_{(i),np}^4 C_{c,\theta}(s_0,s_1)\,,\qquad  i=1,\ldots,p\,.
\end{equation}
Since
\beao
C_{c,\theta}(s_0,s_1)= \sum_{i=s_0}^{s_1} C_{c,\theta}(i,i)
\eeao
one gets the remarkable property that
\beao
&&a_{np}^{-4}\max_{i=1,\ldots,p} \Big| \la_{(i)}\Big(\sum_{s=s_0}^{s_1}\A_n(s)\A_n(s)'\Big)- Z_{(i),np}^4 C_{c,\theta}(s_0,s_1)\Big|\\
&=&a_{np}^{-4}\max_{i=1,\ldots,p} \Big|\sum_{s=s_0}^{s_1}\la_{(i)}(\A_n(s)\A_n(s)')- Z_{(i),np}^4 C_{c,\theta}(s_0,s_1)\Big|+o_P(1)\,.
\eeao
In particular, for $s_1\ge s_0$ we get the weak \con\ of the \pp es towards a PRM:
\beao
&& \sum_{i=1}^p \varepsilon_{a_{np}^{-4}\Big(\la_{i}\Big(\sum_{s=s_0}^{s_0}\A_n(s)\A_n(s)'\big)\,,\ldots,\la_{i}\big(\sum_{s=s_0}^{s_1}\A_n(s)\A_n(s)'\big)\Big)} \\
&\std&
\sum_{i=1}^\infty \varepsilon_{\Gamma_i^{-4/\alpha} \Big(C_{c,\theta}(s_0,s_0),\ldots,C_{c,\theta}(s_0,s_1)\Big)}\,.
\eeao
